Progress

### 2018-07-18 two_dim_majoranas_report/progress.tex
Add SimulationSet object

@@

	 We see that width of the gapless strips along the topological borders are quite wide, requiring very high magnetic field to reach a gapped topological state of the system.
	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|}
			\hline 
			$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
			\hline 
			250 & 1.05 \\ 
			\hline 
			500 & 0.523 \\ 
			\hline 
			1000 & .262 \\ 
			\hline 
			5000 & .0523 \\ 
			\hline 
		\end{tabular} 
		\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
		\label{table:thouless}
	\end{table}

@@

		In figure \ref{fig:muZnosc}, we plot the system without magnetic field in the leads. With respect to the system with zeeman in the leads, it almost seems like the plot has undergone rescaling. The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown). We also see that although we can clearly see the gap closing bands(topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.

@@

	The influence of varying spin orbit coupling seems to be limited. Although at lower spin orbit couplings, we see strands of gap-closings, which would be interesting to investigate, the energy gap in the topological region does not vary much.
		\begin{figure}[H]
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a30.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a33.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a36.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a40.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a43.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a46.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a50.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a53.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a56.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
			\caption{Phase zeeman topology plot with increasing spin orbit. $L_\text{m}=500$nm}
			\label{fig:pfaf_pB_soi}
		\end{figure}

		\begin{figure}[H]
			\begin{tabular}{ccc}
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha10.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha20.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha30.png}\\
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha40.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha50.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha60.png}\\
			\end{tabular}
			\caption{Phase zeeman energy gap plot with increasing spin orbit. $L_\text{m}=500$nm}
			\label{fig:gap_pB_soi}
		\end{figure}
%------------------%
\newpage	
	\subsection{Varying superconducting gap}
	Increasing the superconducting gap has the effect of reducing the energy gap somewhat. We also again see the appearance of gapless bands through the regions.
		\begin{figure}[H]
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d02.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d045.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d067.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d089.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d11.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d133.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d155.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d178.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d200.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%	
\newpage
	\subsection{Varying temperature}
	We 
		\begin{figure}[H]
			\begin{tabular}{rcc}
				a, T=0.025K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T0025.png}&
				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T0025.png}\\
				\hline
				b, T=0.2K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T02.png}&
				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T02.png}\\
				\hline
				c, T=0.6K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T06.png}&
				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T06.png}\\
				\hline
			\end{tabular}
			\caption{Critical current(maximum minus minimum current) and current versus phase and magnetic field strength, assuming zeeman field does not persists in the superconductor. Width of normal strip is 200nm. Temperatures of a, b and c respectively: 0.025 K, 0.2K, 0.6K}
		\end{figure}

>>>>

		\subsubsection{Anna\&Bas}
		Independence of phase should indeed appear beyond a certain magnetic field, when normal reflection becomes very big. When Zeeman is turned on in leads, in a system with infinite sc leads($L_l, L_r \rightarrow \infty$), only a single half diamond appears.

@@

	 We see that width of the gapless strips along the topological borders are quite wide, requiring very high magnetic field to reach a gapped topological state of the system.
 	\subsubsection{Anna\&Bas}
 	Relation between topological gap and thouless is given in the paper. Investigate what regime we are in(short, long intermediate junction). Higher chemical potential would also be a thing
	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|}
			\hline 
			$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
			\hline 
			250 & 1.05 \\ 
			\hline 
			500 & 0.523 \\ 
			\hline 
			1000 & .262 \\ 
			\hline 
			5000 & .0523 \\ 
			\hline 
		\end{tabular} 
		\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
		\label{table:thouless}
	\end{table}

@@

		In figure \ref{fig:muZnosc}, we plot the system without magnetic field in the leads. With respect to the system with zeeman in the leads, it almost seems like the plot has undergone rescaling. The other diamond chains are not visible in this plot, and only appear when we greatly adjust the axes(not shown). We also see that although we can clearly see the gap closing bands(topological borders) in the gap plots, the underlying gap size does not seem greatly affected by being in topological region or not.
	\subsubsection{Anna\&Bas}
	Experiment was run at very small chemical potential, which could cause you to see discretization of the leads. It also matters whether the system is 2d infinite or not. The diamond chains are caused by gap closings of the different bands. If the system is 2d infinite, the gap is always closed.

@@

	The influence of varying spin orbit coupling seems to be limited. Although at lower spin orbit couplings, we see strands of gap-closings, which would be interesting to investigate, the energy gap in the topological region does not vary much.		\subsubsection{Anna\&Bas}
	Effects seen could be due to not counting chemical potential from the bottom of the band, accounting for the term $\propto m\alpha^2$. Check ifthis is indeed the case. Check if this is indeed the case.

	The gap closing might be due to BD1 symmetry. Note that the phase diagram there is $4\pi$ symmetric. Shifting phase by $\pi$ causes overall gauge of -1. Change gap on left and right lead to break symmetry, see if gap closings persist.

		\begin{figure}[H]
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a30.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a33.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a36.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a40.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a43.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a46.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a50.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a53.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a56.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
			\caption{Phase zeeman topology plot with increasing spin orbit. $L_\text{m}=500$nm}
			\label{fig:pfaf_pB_soi}
		\end{figure}

		\begin{figure}[H]
			\begin{tabular}{ccc}
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha10.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha20.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha30.png}\\
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha40.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha50.png}&
				\includegraphics[width=0.33\textwidth]{\img/spinorbitGap/gap_pB_alpha60.png}\\
			\end{tabular}
			\caption{Phase zeeman energy gap plot with increasing spin orbit. $L_\text{m}=500$nm}
			\label{fig:gap_pB_soi}
		\end{figure}
%------------------%
\newpage	
	\subsection{Varying superconducting gap}
	Increasing the superconducting gap has the effect of reducing the energy gap somewhat. We also again see the appearance of gapless bands through the regions.

	\subsubsection{Anna\&Bas}
	Increase width of leads, and rerun experiments. It is weird that gap would decrease as $\Delta$ is increased. Look at band structure.
		\begin{figure}[H]
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d02.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d045.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d067.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d089.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d11.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d133.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d155.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d178.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d200.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%	
\newpage
	\subsection{Varying temperature}
	\subsubsection{Anna\&Bas}
	It is normal to see non block wave phase minimizing current. The current can be split into two contributions. 
	Due to spin orbit coupling, in 2d infinite system, we have two circular fermi surfaces. The values for $\kx,\ky$ which lie on both fermi surfaces, are responsible for the block wave pattern. The region outside of that is responsible for a more sinosoidal pattern.
	So for low spin orbit coupling, the radii are almost the same, and it is all block wave.
		\begin{figure}[H]
			\begin{tabular}{rcc}
				a, T=0.025K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T0025.png}&
				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T0025.png}\\
				\hline
				b, T=0.2K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T02.png}&
				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T02.png}\\
				\hline
				c, T=0.6K&\includegraphics[width=0.4\textwidth]{\img/current/critcurr_lm200_T06.png}&
				\includegraphics[width=0.4\textwidth]{\img/current/curr_lm200_T06.png}\\
				\hline
			\end{tabular}
			\caption{Critical current(maximum minus minimum current) and current versus phase and magnetic field strength, assuming zeeman field does not persists in the superconductor. Width of normal strip is 200nm. Temperatures of a, b and c respectively: 0.025 K, 0.2K, 0.6K}
		\end{figure}
